---
title: "Outlier Detection in Non-Stationary Data Streams"
author: "Priyanga Dilini Talagala"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction


`oddstream` (Outlier Detection in Data STRAMs) is an R package to detect outlying series within a large collection of time series in the context of non-stationary streaming data. We define an outlier as an observation that is very unlikely given the recent distribution of a given system. In this work we make two fundamental contributions. First, we propose a framework that provides early detection of anomalous behaviour within a large collection of streaming time series data using extreme value theory. Second, we propose
a novel approach for early detection of non-stationarity (also called \concept drift"
in the machine learning literature.) The proposed algorithm uses time series fea-
tures as inputs, and a density-based comparison to detect any significant change in
the distribution of the features. 

This vignette documents how to detect anomalous event within a large collection of streaming signals.


## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
